---
title: "An Interpretable Linear Regression Demo"
author: "Hendra Bunyamin"
date: "4/8/2021"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, highlight = TRUE)
```

We set the __working directory__.
```{r message=FALSE, warning=FALSE, highlight=TRUE}
setwd("/home/hbunyamin/Projects/2021-nuni-it-online-seminar/tahun-2021/codes/demo-interpretable-ml")
```
     
Let's load the dataset [@molnar2019].    
```{r message=FALSE, warning=FALSE, highlight=TRUE}
load("bike.RData")
```
     
We view the first five rows.
```{r message=FALSE, warning=FALSE, highlight=TRUE}
head(bike)
```
We summarize the `bike` dataset as follows:
```{r warning=FALSE, message=FALSE, highlight=TRUE}
summary(bike)
```

We extract the features columns just like in the slides as follows:
```{r message=FALSE, warning=FALSE, highlight=TRUE}
bike_to_interpreted <- bike[c("cnt", "season", "holiday", "days_since_2011", 
                         "workingday", "weathersit", "temp", "hum", "windspeed")]
```
      
We summarize the `bike_to_interpreted` dataset.    
```{r message=FALSE, warning=FALSE, highlight=TRUE}
summary(bike_to_interpreted)
```
   
At last, we create the _interpretable linear model_ that is **linear regression** as follows:
```{r message=FALSE, warning=FALSE, highlight=TRUE}
lm_bike <- lm(cnt ~ ., data=bike_to_interpreted)
```


We show the details of the linear models as follows:
```{r message=FALSE, warning=FALSE, highlight=TRUE}
summary(lm_bike)
```

We probably need to install the `dotwhisker` and `dply` packages. Specifically, with `dotwhisker` we can view the weights of our linear model. Alternatively, we can call `coef-plot.R` function.
```{r message=FALSE, warning=FALSE, highlight=TRUE}
library(dotwhisker)
library(dplyr)
dwplot(lm_bike, 
       vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2)) + xlab("Weight estimate")
```

We can load the following R codes consisting several functions for showing the _interpretability of our linear regression_ model.
```{r message=FALSE, warning=FALSE, highlight=TRUE}
source("utils.R", encoding = "UTF-8")
source("ggplot-theme.R", encoding = "UTF-8")
source("effect-plot.R", encoding = "UTF-8")
source("coef-plot.R", encoding = "UTF-8")
```

Let's display the **effect plot** of our model. 
```{r message=FALSE, warning=FALSE, highlight=TRUE}
effect_plot(lm_bike, bike_to_interpreted)
```

Let's display the **coefficient plot** of our model.
```{r message=FALSE, warning=FALSE, highlight=TRUE}
coef_plot(lm_bike)
```
      
Let's load the `cervical` dataset [@molnar2019].    
```{r message=FALSE, warning=FALSE, highlight=TRUE}
load("cervical.RData")
```
  
Let us view the first five rows.  
```{r}
head(cervical)
```

We convert the `Biopsy` column into binary values (`1 = Cancer` and `0 = Healthy`).

```{r}
cervical$Biopsy <- ifelse( cervical$Biopsy == "Healthy", 0, 1  )
```


```{r}
cervical_to_interpreted <- cervical[c("Hormonal.Contraceptives", "Smokes", "Num.of.pregnancies", "STDs..Number.of.diagnosis", 
                         "IUD", "Biopsy")]

```


Let us model the `cervical_to_interpreted` dataset by using logistic regression.

```{r}
lr_cervical <- glm(Biopsy ~ ., data=cervical_to_interpreted, family = binomial(link = "logit"))
```

Let us examine the model's summary.

```{r}
summary(lr_cervical)
```


      
      
# References